Visualizations for the manuscript

### 2022-05-21 metanalysis_visualization/manuscript_Figures.Rmd
Tweaking sex ratio figure

pvalues_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Female proportion since pandemic coefficient: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 2, eps = 10**-2), ")")
  )

@@

#### Table with bootstrapped coefficients, and pvalues

```{r}
pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-2), ")")) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope) %>% 
  flextable::flextable() %>% 
  flextable::save_as_docx(path = "table_sex.docx")

@@

```{r bootstrap_plot}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.005) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

@@

#### Alternative plot 
```{r, include=FALSE}
#plot_annotations_sex_df2 <- data.frame(term=c("difference_solpe","difference_solpe"),
#                                       sex=c("female", "male"),
#                                       label=c("Coefficient difference: 0.77 (pvalue: <0.01)", "Coefficient difference: -0.77 (pvalue: 0.005)"),
#                                       plotsLabel=c("Female", "Male"))

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = label_wrap_gen(width = 35,multi_line = TRUE)) +
  geom_line(aes(color = period),
            alpha = 0.03) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = cbPalette) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 8),
        axis.text.y = element_text(size = 8), 
        axis.title.x = element_text(size = 8),
        axis.title.y = element_text(size = 8),
        title = element_text(size = 14),
        plot.subtitle = element_text(size = 8, face = "italic"), 
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 25, units = "cm")
```

>>>>

pvalues_boot_sex <- bootstrapped_coefficients_sex %>% 
  group_by(sex, term) %>% 
  group_modify( bootstrap_pvalue_calculation, .keep = TRUE) %>% 
  mutate(label = paste0("Coefficient difference: ",
                        observed_slope_coefficient,
                        " (pvalue: ",
                        format.pval(pvalue, digits = 3, eps = 10**-3), ")")
  )

@@

```
↨
#### Table with bootstrapped coefficients, and pvalues

```{r}
pvalues_boot_sex %>% 
  inner_join(ci_boot_sex) %>% 
  arrange(sex) %>% 
  mutate(string = paste0(observed_slope_coefficient, " ", ci, " (", format.pval(pvalue, digits = 3, eps = 10**-3), ")")) %>% 
  select(sex, string) %>% 
  pivot_wider(names_from = term, values_from = string) %>% 
  select(sex, before_slope, during_slope, difference_slope) %>% 
  rename("Before pandemic trend [95% CI] (p-value)" = before_slope,
        "Since pandemic trend [95% CI] (p-value)" = during_slope,
        "Difference before/since pandemic trend [95% CI] (p-value)" = difference_slope) %>% 
  flextable::flextable() %>% 
  flextable::save_as_docx(path = "table_sex.docx")

@@

```{r }
#plot_annotations_sex_df2 <- data.frame(term=c("difference_solpe","difference_solpe"),
#                                       sex=c("female", "male"),
#                                       label=c("Coefficient difference: 0.77 (pvalue: <0.01)", "Coefficient difference: -0.77 (pvalue: 0.005)"),
#                                       plotsLabel=c("Female", "Male"))

bootstrapped_fitted_sex %>% 
  filter( sex == "female") %>%
  mutate(period = recode_factor(period, "before_pandemic" = "Before pandemic onset", "during_pandemic" = "Since pandemic onset")) %>% 
  ggplot(aes(x = time_p, y = predicted, group = interaction(iteration, period))) +
  facet_wrap("sex",
             labeller = labeller(sex = c("female" = "Female proportion "))) +
  geom_line(aes(color = period),
            alpha = 0.01) +
  geom_line(data = quantile_bootstrapped_fitted_sex[ quantile_bootstrapped_fitted_sex$sex =="female", ],
            aes(y = value, group = interaction(quantiles, period)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$sex =="female" & quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value, group = period)) +
  geom_point(data = patients_hospitalized_agg_sex_total[ patients_hospitalized_agg_sex_total$sex =="female",],
             aes(y = percentage, group=NULL),
             alpha = 0.5) +
  scale_colour_manual(values = wesanderson::wes_palette("GrandBudapest1", 3)) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(color = guide_legend(override.aes = list(alpha = 1))) +
  geom_label(data = plot_annotations_sex_df, 
             aes(label=label), 
            x = -Inf,
            y = +Inf,
            hjust = 0,
            vjust = 1,
            size = 4,
            inherit.aes = FALSE) +
  labs(x = "Calendar dates",
       y = "Percentage",
       color = "Period") +
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"),
        legend.position = "bottom") 
ggsave("figure4_boostrapped_sex.png", height = 15, width = 20, units = "cm")
```

### Alternative plot

```{r bootstrap_plot, include=FALSE}
plot_sex <- ggplot(bootstrapped_fitted_sex,
       aes(x = time_p, y = predicted/100, group = interaction(iteration, period, sex))) +
  geom_line(aes(color = interaction(period, sex)),
            alpha = 0.005) +
  geom_line(data = quantile_bootstrapped_fitted_sex,
            aes(y = value/100, group = interaction(quantiles, period, sex)),
            linetype = "dashed") +
  geom_line(data = quantile_bootstrapped_fitted_sex[quantile_bootstrapped_fitted_sex$quantiles == "50%", ],
            aes(y = value/100, group = interaction(period, sex))) +
  geom_point(data = patients_hospitalized_agg_sex_total,
             aes(y = percentage/100, group=sex),
             alpha = 1) +
  # scale_color_brewer(palette = "Paired") +
  scale_color_manual(labels = c("Female", "Male", "", ""),
                     values = c("#A6CEE3", "#1F78B4", "#B2DF8A", "#33A02C")) +
  scale_x_date(breaks = "1 month", labels=date_format("%b-%y"), expand=c(0.03,0))+
  guides(colour = guide_legend(
    override.aes = list(alpha = 1,
                        colour = c('#1F78B4', '#33A02C', NA, NA))) 
  ) +
  #geom_label(data = plot_annotations_sex_df,
  #           aes(label = label),
  #           x = -Inf,
  #           y = +Inf,
  #           hjust = 0,
  #           vjust = 1,
  #           size = 4,
  #           inherit.aes = FALSE) +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.69,
           #label = "Female proportion", 
           label = "Female proportion [Coefficient difference: 0.77 (pvalue: <0.01)]", 
           fill = "#A6CEE3") +
  annotate("label",
           x = as.Date('2019-10-01'),
           y = 0.3,
           #label = "Male proportion", 
           label = "Male proportion [Coefficient difference: -0.77 (pvalue: 0.005)]", 
           fill = "#B2DF8A") +
  # annotate("text", x = 7, y = 0.15, label = "Male proportion") +
  labs(
    #title = "Patients sex proportion trends among psychiatric-related visits",
    #   subtitle = "Parametric bootstrap estimation: (10000 iterations)",
       x = "Calendar dates",
       y = "Sex proportion",
       color = "Sex") +
  ylim(0.25, 0.75) + 
  theme(strip.text = element_text(size = 10),
        axis.text.x=element_text(angle = 45, hjust=1, size = 10),
        axis.text.y = element_text(size = 10),
        axis.title.x = element_text(size = 10),
        axis.title.y = element_text(size = 10),
        title = element_text(size = 14), 
        plot.subtitle = element_text(size = 12, face = "italic"))

@@
